Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-13 blind.tex
Add discussion notes
Handle action items

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.

\Ethan{How to work the security parameter into the following? It's annoying if everything takes that.
Also, where do I write that footnote about extra uncompiled inputs such as accuracy param.?}

@@

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating \linebreak
			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by \linebreak
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$
				Then it applies the next-message function homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

>>>>

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For the sake of simplicity, we omit the security and accuracy parameters. \Ethan{The previous sentence is newly added}
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.

@@

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating %\linebreak
			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow  \QEval(pk, \cP_1,$ \  $\ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec,$ \ $\ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
				Then it applies the next-message function homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

### 2020-04-13 preliminaries.tex
Handle action items

\Ethan{Sec. param. should be 1st param}

\begin{definition}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds.
\begin{itemize}
		\item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
		\item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
		$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
		\item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
	\end{itemize}
\end{definition}

\begin{definition}
	\label{dfn:stats-secure-proto-sampbqp}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness if the following holds.
	\begin{itemize}
		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^n$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. If $d=\Acc$ then $z\in\zo^{m(n)}$, otherwise $z=\bot$.
		\item (Completeness):
			For all security parameter $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item (Statistical soundness): For all cheating prover $P^*$,
			sufficiently large $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
			consider the following experiment:
			\begin{itemize}
				\item Let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
				\item Define $z_{ideal}$ by
				$$\begin{cases}
					z_{ideal}=\bot & \text{if } d=\Rej\\
					z_{ideal}\leftarrow D_x & \text{if } d=\Acc
				\end{cases}$$.
			\end{itemize}
			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
		\item (Computational soundness): Define $d, z, z_{ideal}$ same as above.
			It holds that for all $\BQP$ distinguisher $D$,
			$\abs{\Pr[D(1^{\lambda}, d,z) = 1] - \Pr[D(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $
	\end{itemize}
\end{definition}

We define blindness of a protocol as follows. \Ethan{Input x is private input now... the rest are still common input... etc.}

\begin{definition}
	Let $(P, V)$ be an interactive protocol with security parameter $\lambda$. \Ethan{Define the version with eps, say that it's fine without eps for BQP} \Ethan{TODO Quantify cheating prover}
	Let $\lambda$ be a security parameter.
	Then it is \emph{blind} if the following ensembles are computationally indistinguishable over $\lambda$:
	\begin{itemize}
		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
	\end{itemize}
\end{definition}

@@

\Ethan{Just define QHE}

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client. We start by presenting the definition of a homomorphic encryption scheme:
\begin{definition}
    \Ethan{Do more copying}
	A leveled homomophic encryption scheme is tuple of algorithms \linebreak $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{HE.Keygen}(1^\lambda, 1^L)\rightarrow(pk, sk)$
		\item $\mathsf{HE.Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{HE.Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{definition}

$\mathsf{HE}$ also satisfies, with overwhelming probability in $\lambda$, that
$$\mathsf{HE.Dec}_{sk}(\mathsf{HE.Eval}_{pk}(f, c_1, \ldots, c_l))=f(\mathsf{HE.Dec}_{sk}(c_1),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$
where $f$ is specified by a circuit of depth at most $L$.

\Ethan{To be pedantic, the above doesn't imply Dec undoes Enc even if we sub in $f=\id$.}

\Ethan{Maybe add correctness}

@@

\begin{definition}
	A FHE scheme $\mathsf{HE}$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda)$$
	where $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^\lambda)$
\end{definition}

@@

\begin{definition}
	we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:
	\begin{itemize}
		\item $\QGen$ produces classical keys
		\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
		\item Its ciphertext can be homomorphically measured, after which $\QDec$ can also be done classically. \Ethan{Underlying msg is classical = ct is classical = can be classical decrypted}
	\end{itemize}
\end{definition}

>>>>

\begin{definition}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a prototol for a $\BQP$ language $L$ with completeness error $c(\cdot)$ and soundness error $s(\cdot)$ if the following holds:
\begin{itemize}
		\item On public inputs $1^\lambda$ and $x\in\zo^*$, the verifier outputs either $\Acc$ or $\Rej$.
		\item (Completeness): For all security parameter $\lambda\in\bbN$ and $x\in\zo^{\poly(\lambda)}$, if $x\in L$ then
		$\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
		\item (Soundness): For all cheating $\BQP$ prover $P^*$, sufficiently large security parameter $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, if $x \notin L$ then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<s(\lambda)$.
	\end{itemize}
\end{definition}

\begin{definition}
	\label{dfn:stats-secure-proto-sampbqp}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c$ and statistical (resp., computational) soundness if the following holds:
	\begin{itemize}
		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^n$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. If $d=\Acc$ then $z\in\zo^{m(n)}$, otherwise $z=\bot$.
		\item (Completeness):
			For all security parameter $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item (Statistical soundness): For all cheating prover $P^*$,
			sufficiently large $\lambda\in\bbN$, accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$, and $x\in\zo^{\poly(\lambda)}$, 
			consider the following experiment:
			\begin{itemize}
				\item Let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
				\item Define $z_{ideal}$ by
				$$\begin{cases}
					z_{ideal}=\bot & \text{if } d=\Rej\\
					z_{ideal}\leftarrow D_x & \text{if } d=\Acc
				\end{cases}$$.
			\end{itemize}
			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
		\item (Computational soundness): Define $d, z, z_{ideal}$ same as above.
			It holds that for all $\BQP$ distinguisher $D$,
			$\abs{\Pr[D(1^{\lambda}, d,z) = 1] - \Pr[D(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $
	\end{itemize}
\end{definition}

We now define blindness of a protocol.
In the context of blind protocols, the above definitions should be modified so that $x$ is the verifier's private input.
We define blindness with an accuracy parameter $\varepsilon$, which exists in protocols for $\SampBQP$ instances;
one can leave it out where appropriate, such as in protocols for $\BQP$ languages.

\begin{definition}
	Let $\Pi=(P, V)$ be an interactive protocol with common inputs $1^\lambda$ and $1^{1/\varepsilon}$, and verifier's private input $x\in\zo^*$.
	We say $\Pi$ is \emph{blind} if for all cheating prover $P^*$ the following ensembles are computationally indistinguishable over $\lambda$:
	\begin{itemize}
		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda, 1^{1/\varepsilon})}_{\lambda\in\bbN, \varepsilon\in(0,1), x\in\zo^*}$
		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda, 1^{1/\varepsilon})}_{\lambda\in\bbN, \varepsilon\in(0,1), x\in\zo^*}$
	\end{itemize}
\end{definition}

@@

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
\begin{definition}
	A quantum homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
	$\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
	\begin{itemize}
		\item \emph{Key generation.}
			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda)$ takes a unary representation of the security parameter and outputs a public key encryption key $pk$ and a secret decryption key $sk$.
		\item \emph{Encryption.}
			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ and outputs a ciphertext $c$.
		\item \emph{Decryption.}
			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ and outputs a message $\mu^*\in\zo$.
			It must be the case that
				$$\QDec(sk, \QEnc(pk, \mu))=\mu$$
			with overwhelming probability in $\lambda$.
		\item \emph{Homomorphic Evaluation.}
			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit \Ethan{?} $f$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ and outputs a ciphertext $c_f$.
			It must be the case that
				$$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
			with overwhelming probability in $\lambda$.
	\end{itemize}
\end{definition}

\begin{definition}[Compactness and Full Homomorphism]
	\Ethan{This is copied from Mahadev. Not sure how much of this we need. We need at least how leveled HE is defined.}

	A quantum homomorphic encryption scheme $\QHE$ is compact if
	there exists a polynomial $s$ in $\lambda$ such that the output length of $\QEval$ is at most $s$ bits long (regardless of $f$ or
	the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
	boolean function. A compact scheme is leveled fully homomorphic if it takes $1^L$ as additional input in key generation,
	and can only evaluate depth $L$ Boolean circuits where $L$ is polynomial in $\lambda$. A scheme is quantum pure or
	leveled fully homomorphic if we refer to quantum circuits rather than boolean circuits.
\end{definition}

@@

\begin{definition}
	\Ethan{This was copied from Mahadev. Not sure where $L$ (level) goes.}
	A scheme $\QHE$ is IND-CPA secure if, for any polynomial time adversary $\cA$, there exists a negligible function $\mu(\cdot)$ such that
	$$\abs{Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(0))=1]-Pr[\cA(pk, \mathsf{HE.Enc}_{pk}(1))=1]}\leq\mu(\lambda)$$
	where $(pk, sk)\leftarrow\QGen(1^\lambda)$
\end{definition}

@@

\begin{definition}
	we call a quantum homomorphic encryption scheme \emph{classical-friendly} if it has the following properties:
	\begin{itemize}
		\item $\QGen$ produces classical keys
		\item In the case where the plaintext is classical, $\QEnc$ can be done classically.
		\item When the underlying message is classical, the corresponding ciphertext is also classical and can be decrypted classically.
	\end{itemize}
\end{definition}
